%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn

\usepackage[titletoc]{appendix}
\usepackage{float}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{courier}
% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography

\usepackage[utf8]{inputenc}
\usepackage[greek,english]{babel}
\usepackage{lmodern}	

\usepackage{mathtools, nccmath}
\usepackage[nottoc]{tocbibind} % bind bibliography to the table of contents
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\usepackage[table]{xcolor}


\hypersetup{urlcolor=black, colorlinks=true}  % Colours hyperlinks in black, can be distracting if there are many links and colored blue.

\makeatletter
\let\c@table\c@figure % for (1)
\let\ftype@table\ftype@figure % for (2)
\makeatother

%% ----------------------------------------------------------------

\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {Real-Time Monitoring of Message-Driven Data Pipelines}
\authors  {John McAleer}
            
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}


\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers
%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here


\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, John McAleer, declare that this proposal titled, `Real-Time Monitoring of Message-Driven Data Pipelines' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for an masters degree at Cork Institute of Technology.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this project report is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] I understand that my project documentation may be stored in the library at CIT, and may be referenced by others in the future.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------

% The Abstract Page

\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents

\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

The Message-Driven Architecture (MDA), a subset of the Service-Oriented Architecture (SOA), is an architectural pattern applied to the design of applications comprising loosely-coupled software components which communicate over a messaging system. Message-driven applications  comprise sets of message producers, message consumers and message sinks, communicating over a set of message channels. The decoupling inherent to message-driven applications provides a high degree of structural malleability; message producers are unaware of message consumers, enabling the addition and removal of software components with minimal impact. This architecture is commonly employed in the implementation of data pipelines, systems which comprise multiple services responsible for the ingestion, validation, transformation and processing of continuous streams of data.

Given the decoupled and flexible nature of the Message Driven Architecture, identification of the set of services comprising a pipeline, the communication paths between same, and the characteristics of runtime service intercommunication at a point in time may present a number of difficulties. Developers, testers, and maintainers of message-driven pipeline applications face such challenges during all stages of the development and production life-cycle. 

This thesis explores contemporary practices and technologies in the area of message-driven pipeline monitoring. The technical challenges inherent to the design and implementation of a real-time monitoring solution are explored. A technology-agnostic monitoring application is developed and successfully applied to an Apache Kafka-based messaging pipeline. 



\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

The author wishes to express wholehearted appreciation to Dr. Donna Griffin of the CIT Computer Science Department for her assistance and guidance in the development of this dissertation from concept to submission, and to Mr. Larkin Cunningham for his valuable feedback.
}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
	% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
	\textbf{API} & \textbf{A}pplication \textbf{P}rogramming \textbf{I}nterface \\
	\textbf{CEP} & \textbf{C}omplex \textbf{E}vent \textbf{P}rocessing  \\
	\textbf{CRUD} & \textbf{C}reate, \textbf{R}etrieve, \textbf{U}pdate, \textbf{D}elete \\
	\textbf{CPU} & \textbf{C}entral \textbf{P}rocessing \textbf{U}nit \\
	\textbf{DAO} & \textbf{D}ata \textbf{A}ccess \textbf{O}bject \\
	\textbf{DTO} & \textbf{D}ata \textbf{T}ransfer \textbf{O}bject \\
	\textbf{HTTP} & \textbf{H}yper\textbf{T}ext \textbf{T}ransfer \textbf{P}rotocol \\
	\textbf{IoT} & \textbf{I}nternet \textbf{o}f \textbf{T}hings \\
	\textbf{ITOM} & \textbf{IT} \textbf{O}perations \textbf{M}anagement \\
	\textbf{JMX} & \textbf{J}ava \textbf{M}anagement \textbf{E}xtensions \\
	\textbf{JPA} & \textbf{J}ava \textbf{P}ersistence \textbf{A}PI \\
	\textbf{JSON} & \textbf{J}ava\textbf{S}cript \textbf{O}bject \textbf{N}otation \\
	\textbf{MDA} & \textbf{M}essage-\textbf{D}riven \textbf{A}rchitecture \\
	\textbf{ML} & \textbf{M}achine \textbf{L}earning \\
	\textbf{MSA} & \textbf{M}icro\textbf{S}ervice \textbf{A}rchitecture \\
	\textbf{OCL} & \textbf{O}bject \textbf{C}onstraint \textbf{L}anguage \\
	\textbf{REST} & \textbf{RE}presentational \textbf{S}tate \textbf{T}ransfer \\
    \textbf{SARESA} & \textbf{S}sense \textbf{A}nd \textbf{RE}sponse  \textbf{S}ervice \textbf{A}rchitecture\\
	\textbf{SOA} & \textbf{S}service-\textbf{O}riented \textbf{A}rchitecture \\	
	\textbf{UI} & \textbf{U}ser \textbf{I}nterface \\
	\textbf{URL} & \textbf{U}niform \textbf{R}esource \textbf{L}ocator \\
	\textbf{UUID} & \textbf{U}niverally  \textbf{U}nique \textbf{I}dentifier \\	
}

%% ----------------------------------------------------------------
\clearpage  % Start a new page


%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3

\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{Dedicated to Niamh, Frieda and Roisin; to their boundless patience and light spirits.}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics

%%


\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

\input{Chapters/Introduction} % Introduction

\input{Chapters/Background} % Introduction

\input{Chapters/RequirementsAndDesign} % Requirements and Design

\input{Chapters/SoftwareImplementation} 

\input{Chapters/SoftwareWalkthrough} 

\input{Chapters/Conclusion} 

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}
\bibliographystyle{IEEEtranN}  % Use the "IEEE Transaction" BibTeX style for formatting the Bibliography
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\begin{appendices}
	
\input{Appendices/AppendixA}
\input{Appendices/AppendixB}  

\end{appendices}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter
\end{document}  % The End
%% ----------------------------------------------------------------